\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-14 paper.qmd
Added high-d model error in 2D s-curve

>>>>

```{r}
#| label: best-umap-model-scurve

```{r}
#| label: p-d-error-in-2d-scurve

## Compute error
error_df_scurve <- augment(
  df_bin_centroids = df_bin_centroids_scurve,
  df_bin = df_bin_scurve,
  training_data = training_data_scurve,
  newdata = NULL,
  type_NLDR = "UMAP",
  col_start = "x")

error_df_scurve <- error_df_scurve |>
  mutate(type = case_when(
    row_wise_abs_error == 0 ~ "no error",
    row_wise_abs_error <= 0.2 ~ "error 0-0.2",
    row_wise_abs_error <= 0.4 ~ "error 0.2-0.4",
    row_wise_abs_error <= 0.6 ~ "error 0.4-0.6",
    .default = "error greter than 0.6"
  )) |>
  mutate(type = factor(type, levels = c(
    "no error", "error 0-0.2", "error 0.2-0.4", "error 0.4-0.6", "error greter than 0.6")))

error_df_scurve <- error_df_scurve |>
  bind_cols(umap_scurve_scaled |>
              select(-ID))

error_plot_scurve <- error_df_scurve |>
  ggplot(aes(x = UMAP1,
             y = UMAP2,
             color = type)) +
  geom_point(alpha=0.5) +
  theme(
    legend.position = "bottom"
  )

error_plot_scurve 
```

### 2024-08-14 paper.tex
Replaced Six to Eight in Figure 1 title
Added axes to the projection: Need to check with the origin
Added high-d model error in 2D s-curve

\caption{\label{fig-NLDR-variety}Six different NLDR representations of
the same data. Different techniques and different parameter choices are
used. Researchers may have seen any of these in their analysis of this
data, depending on their choice of method, or typical parameter choice.
Would they make different decisions downstream in the analysis depending
on which version seen? Which is the most accurate representation of the
structure in high dimensions?}

@@

@@

>>>>

\caption{\label{fig-NLDR-variety}Eight different NLDR representations of
the same data. Different techniques and different parameter choices are
used. Researchers may have seen any of these in their analysis of this
data, depending on their choice of method, or typical parameter choice.
Would they make different decisions downstream in the analysis depending
on which version seen? Which is the most accurate representation of the
structure in high dimensions?}

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/p-d-error-in-2d-scurve-1.pdf}
\end{center}

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-23-1.pdf}
\end{center}
